Evaluating Deep Learning Methods for Tokenization of Space-less texts in Old French and Latin

### 2019-06-08 article/article.tex
Article update

\begin{figure}[!ht]
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
          width=\linewidth, % Scale the plot to \linewidth
          grid=major,
          grid style={dashed,gray!30},
          xlabel=Epoch, % Set the labels
          ylabel=Accuracy,
          legend style={at={(0.5,-0.2)},anchor=north},
          x tick label style={rotate=90,anchor=east}
        ]
        \addplot table[x=Epoch,y=CNN 1,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN L,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN w/o P,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN N,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN L N,col sep=comma] {accuracies.csv};
        \legend{CNN, CNN L, CNN P, CNN N, CNN L N}
      \end{axis}
    \end{tikzpicture}
    \caption{Training Loss (Cross-entropy) until plateau was reached. N = normalized, L = Lower, P = no position embedding. LSTM was removed as it did not go below 0.65}
  \label{fig:loss}
  \end{center}
\end{figure}

\begin{table}[!ht]
\centering
\begin{tabular}{lllllll}
\hline
Model    & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & 0.989    & 0.986     & 0.984  & 0.985 & 4031 & 3229 \\
CNN      & 0.991    & 0.985     & 0.990  & 0.987 & 2137 & 3860 \\
CNN L    & 0.991    & 0.979     & 0.990  & 0.985 & \textbf{2117} & 3750 \\
CNN P    & \textbf{0.993}    & \textbf{0.990}& \textbf{0.991}  & \textbf{0.990} & 2432 & \textbf{2114} \\
CNN N    & 0.991    & 0.987     & 0.988  & 0.988 & 2756 & 3312 \\
CNN L N  & 0.992    & 0.988     & 0.989  & 0.988 & 2500 & 3567 \\
LSTM     & 0.741    & 0.184     & 0.500  & 0.269 & 169094 & 0 \\ \hline
\end{tabular}
\caption{Scores over the test dataset. \\\hspace{\textwidth}For models: N = normalized, L = Lower, P = no position embedding. \\\hspace{\textwidth}In headers, FN = False Negative, FP = False Positive}
\label{tab:scores}
\end{table}

>>>>

\begin{figure}[!ht]
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
          width=\linewidth, % Scale the plot to \linewidth
          grid=major, 
          grid style={dashed,gray!30},
          xlabel=Epoch, % Set the labels
          ylabel=Accuracy,
          legend style={at={(0.5,-0.2)},anchor=north},
          x tick label style={rotate=90,anchor=east}
        ]
        \addplot table[x=Epoch,y=CNN 1,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN L,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN w/o P,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN N,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN L N,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=LSTM,col sep=comma] {accuracies.csv}; 
        \legend{CNN, CNN L, CNN P, CNN N, CNN L N, LSTM}
      \end{axis}
    \end{tikzpicture}
    \caption{Training Loss (Cross-entropy) until plateau was reached. N = normalized, L = Lower, P = no position embedding. LSTM was removed as it did not go below 0.65}
  \label{fig:loss}
  \end{center}
\end{figure}

\begin{table}[!ht]
\centering
\begin{tabular}{lllllll}
\hline
Model    & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & 0.989    & 0.986     & 0.984  & 0.985 & 4031 & 3229 \\
CNN      & 0.991    & 0.985     & 0.990  & 0.987 & 2137 & 3860 \\
CNN L    & 0.991    & 0.979     & 0.990  & 0.985 & \textbf{2117} & 3750 \\
CNN P    & \textbf{0.993}    & \textbf{0.990}& \textbf{0.991}  & \textbf{0.990} & 2432 & \textbf{2114} \\
CNN N    & 0.991    & 0.987     & 0.988  & 0.988 & 2756 & 3312 \\
CNN L N  & 0.992    & 0.988     & 0.989  & 0.988 & 2500 & 3567 \\
LSTM     & 0.939    & 0.637     & 0.918  & 0.720 & 21174 & 18662 \\ \hline
\end{tabular}
\caption{Scores over the test dataset. \\\hspace{\textwidth}For models: N = normalized, L = Lower, P = no position embedding. \\\hspace{\textwidth}In headers, FN = False Negative, FP = False Positive}
\label{tab:scores}
\end{table}
